\chapter{Specifications}\label{ch:specs}

The application developed for this workgroup task is a tool for
\standout{restaurants recommendations providing by a user social
infrastructure}.

The main purpose of the application is to allow restaurant owners to make their
restaurants known to a large number of people and allow the customer to find
the most appreciated restaurant and permit to create a network of friendship
with other users.

An administrator of the applications specifies the available restaurant's
cities and cuisines.

Before login the first time users must register to the application specifying
nickname, password, city where they live, and if they are customers or
restaurant owners. 

When logged in, the \standout{customer} sees the list of his favorite
restaurants and the list of his friends. He/She can put like to other
restaurants or remove like from the the ones into his list. Also he/she can
follow new friends or can unfollow his/her friends. He can also specify the
type of cuisines he is interested in. A customer can view a list of
restaurants that the application recommends, based on number of likes put by
friends (or friends of friends). Recommendations can be filtered considering
the distance between the restaurant and user's city, the cuisine's type and.
The application also can provide advises for new people to follow with same
interests in type of cuisine, based on the number of restaurants they liked.

A \standout{restaurant owner} can add a restaurant (or many), inserting all the
information as the name, the city where is located and the type of cuisine. He
can also modify information whenever he wants. The owner can see the number of
his restaurant's likes and see how his/her restaurants are ranked in the city
where they are located considering all restaurants of the city or considering
restaurants with the same type of cuisine.